Exploratory data analysis

### 2021-10-12 slides/data_checking.Rmd
needs to be cleaned up but started

```{r}
q_google_demos %>% 
  ggplot(aes(x = age, fill = gender)) +
  geom_histogram(position = "identity", alpha = 0.5)
```

@@

@@

```{r}
j_recall %>% 
  ggplot(aes(x = acc_recall, y = resp_conf, color = j_score, fill = j_score)) + 
  geom_jitter(alpha = 0.3, width = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "lm", formula = y ~ x, se = FALSE) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  labs(x = "Recall accuracy (strict)", y = "Recall confidence", color = "Expertise score", fill = "Expertise score") +
  theme_bw()
```

@@

```{r}
j_recall %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  mutate(acc_recall = as.integer(acc_recall),
         # so 0.5 is centered
         j_score = j_score - 0.5,
         is_male = gender == "male") %>% 
  lme4::lmer(resp_conf ~ acc_recall * j_score + is_male + (1 + acc_recall | subj_num), data = .) %>% 
  summary()
```

@@

```{r}
j_recall %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  ggplot(aes(x = resp_conf, y = as.integer(acc_recall), color = gender, fill = gender)) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), se = FALSE) +
  labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
  theme_bw()
```

@@

```{r}
j_recall %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  ggplot(aes(x = acc_recall, y = resp_conf, color = gender)) + 
  geom_jitter(alpha = 0.3, width = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "lm", formula = y ~ x, se = FALSE, size = 0.5) + 
  labs(x = "Recall accuracy (strict)", y = "Recall confidence", color = "Expertise score", fill = "Expertise score") +
  theme_bw()
```

```{r}
j_recall %>% 
  ggplot(aes(x = rt_end_recall, y = as.integer(acc_recall), color = j_score, fill = j_score)) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  labs(x = "Recall submit RT", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  # filter(!is.na(already_knew)) %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = resp_pic, y = acc_recall, color = j_score, fill = j_score)) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  # facet_grid(~already_knew) +
  labs(x = "Photo recognition accuracy", y = "Fact recall accuracy (generous)") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         interest = (interest / 100) - 0.5,
         j_score = j_score - 0.5) %>% 
  lme4::glmer(acc_recall ~ interest * j_score + (1 | subj_num), data = ., family = "binomial") %>% 
  summary()
```

@@

@@

@@

@@

```{r}
retrieval %>% 
  ggplot(aes(x = interest, y = resp_pic, color = j_score, fill = j_score)) + 
  geom_point(alpha = 0.3) + 
  geom_smooth(aes(group = subj_num), method = "lm", se = FALSE) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  labs(x = "Interest in fact at encoding", y = "Photo recognition accuracy") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  ggplot(aes(x = interest, y = resp_source, color = j_score, fill = j_score)) + 
  geom_point(alpha = 0.3) + 
  geom_smooth(aes(group = subj_num), method = "lm", se = FALSE) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  labs(x = "Interest in fact at encoding", y = "Source recognition accuracy") +
  theme_bw()
```

>>>>

```{r}
q_google_demos %>% 
  ggplot(aes(x = age, fill = gender)) +
  geom_histogram(position = "identity", alpha = 0.5, binwidth = 2)
```

@@

### What is our sample spread of trivia expertise?

```{r}
j_exp %>% 
  ggplot(aes(x = j_score)) +
  geom_histogram() +
  geom_vline(xintercept = 0.7, linetype = "dotted")
```

@@

### Better experts tend to be more confident

This effect does not necessarily imply that better experts are _overconfident._ Rather, it is consistent with better experts tending to have higher latent knowledge for each question, and thus being likely to be more confident overall, even when the answer turns out to be wrong.

```{r}
j_recall %>% 
  group_by(subj_num, j_score) %>% 
  summarize(conf_q500 = median(resp_conf, na.rm = TRUE),
            conf_q250 = quantile(resp_conf, .25, na.rm = TRUE),
            conf_q750 = quantile(resp_conf, .75, na.rm = TRUE),
            conf_q025 = quantile(resp_conf, .025, na.rm = TRUE),
            conf_q975 = quantile(resp_conf, .975, na.rm = TRUE)) %>% 
  ggplot(aes(x = subj_num, y = conf_q500, color = j_score)) +
  # geom_errorbar(aes(ymin = conf_q025, ymax = conf_q975), width = 0, size = 0.5) +
  geom_errorbar(aes(ymin = conf_q250, ymax = conf_q750), width = 0, size = 1) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_viridis_c() +
  theme_bw() +
  theme(axis.text.y = element_blank())
```

@@

@@

```{r}
j_recall %>% 
  ggplot(aes(x = rt_end_recall, y = as.integer(acc_recall), color = j_score, fill = j_score)) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), se = FALSE) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  labs(x = "Recall submit RT", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
  theme_bw()
```

@@

### Better experts tend to respond faster

Again, this is consistent with an across-participants tendency to respond faster for subsequently correct answers. Better experts who are giving more correct answers are thus more likely to have shorter RTs.

```{r}
j_recall %>% 
  group_by(subj_num, j_score) %>% 
  summarize(rt_q500 = median(rt_end_recall, na.rm = TRUE),
            rt_q250 = quantile(rt_end_recall, .25, na.rm = TRUE),
            rt_q750 = quantile(rt_end_recall, .75, na.rm = TRUE),
            rt_q025 = quantile(rt_end_recall, .025, na.rm = TRUE),
            rt_q975 = quantile(rt_end_recall, .975, na.rm = TRUE),
            rt_mean = mean(rt_end_recall, na.rm = TRUE),
            rt_sd = sd(rt_end_recall, na.rm = TRUE)) %>% 
  ggplot(aes(x = subj_num, y = rt_mean, color = j_score)) +
  geom_errorbar(aes(ymin = rt_mean - rt_sd/2, ymax = rt_mean + rt_sd/2), width = 0, size = 1) +
  geom_point(size = 3) +
  coord_flip() +
  scale_color_viridis_c() +
  theme_bw() +
  theme(axis.text.y = element_blank())
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = resp_pic, y = acc_recall, color = j_score, fill = j_score)) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.02) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  # facet_grid(~already_knew) +
  labs(x = "Photo recognition accuracy", y = "Fact recall accuracy (generous)") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = resp_pic, y = acc_recall, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
  labs(x = "Photo recognition accuracy", y = "Fact recall accuracy (generous)") +
  theme_bw()
```

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         resp_pic = resp_pic / 100,
         j_score = j_score - 0.5) %>% 
  lme4::glmer(acc_recall ~ resp_pic * j_score + (1 | subj_num), data = ., family = "binomial") %>% 
  summary()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall),
         j_score_binary = j_score > 0.72) %>%
  ggplot(aes(x = resp_source, y = acc_recall, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
  labs(x = "Source recognition accuracy", y = "Fact recall accuracy (generous)") +
  theme_bw()
```

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         resp_source = resp_source / 100,
         j_score = j_score - 0.5) %>% 
  lme4::glmer(acc_recall ~ resp_source * j_score + (1 | subj_num), data = ., family = "binomial") %>% 
  summary()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  ggplot(aes(x = resp_source, y = resp_pic, color = cut_number(j_score, 5), fill = cut_number(j_score, 5))) + 
  geom_point(alpha = 0.1) + 
  geom_smooth( method = "lm", alpha = 0.2) + 
  labs(x = "Source recognition accuracy", y = "Photo recognition accuracy") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = interest, y = acc_recall, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
  labs(x = "Interest in fact at encoding", y = "Fact recall accuracy (generous)") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  # filter(already_knew == "none") %>% 
  ggplot(aes(x = interest, y = resp_pic, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(method = "lm", alpha = 0.2) + 
  labs(x = "Interest in fact at encoding", y = "Photo recognition accuracy") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  ggplot(aes(x = interest, y = resp_source, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
  geom_point(alpha = 0.1) + 
  geom_smooth(method = "lm", alpha = 0.2) + 
  labs(x = "Interest in fact at encoding", y = "Source recognition accuracy") +
  theme_bw()
```
